---
title: "Crude Associations"
author: "Bryon Langford, Matthew Hoctor"
date: "7/20/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (Sys.info()["sysname"] == "Windows") 
  knitr::opts_chunk$set(engine.path = list(stata = "C:/Program Files/Stata17/StataBE-64")) 
if ((Sys.info()["sysname"] == "Darwin"))
  knitr::opts_chunk$set(engine.path = list(stata = "/Applications/Stata/StataIC"))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

# Associations between MJ exposure and covariates

## Gender

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta gndr MJ,col percent
```

## Education

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta EDUC_cat MJ,col percent
```

## Race

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta race_eth MJ,col percent
```

## Survey Year

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta sddsrvyr MJ,col percent
```

## Income

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): mean indfmpir,over(MJ)coeflegend
# svy, subpop(if include==1): mean indfmpir,over(MJ)

test _b[c.indfmpir@0bn.MJ] = _b[c.indfmpir@1.MJ] = _b[c.indfmpir@2.MJ] = _b[c.indfmpir@3.MJ] = _b[c.indfmpir@4.MJ]
```

## Age

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): mean ridageyr,over(MJ)coeflegend
# svy, subpop(if include==1): mean ridageyr,over(MJ)

test _b[c.ridageyr@0bn.MJ] = _b[c.ridageyr@1.MJ] = _b[c.ridageyr@2.MJ] = _b[c.ridageyr@3.MJ] = _b[c.ridageyr@4.MJ]
```

## Smoking

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta SMK_cat MJ,col percent
```

## Alcohol

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta AL_cat MJ,col percent
```

## BMI

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): mean bmxbmi,over(MJ)coeflegend
# svy, subpop(if include==1): mean bmxbmi,over(MJ)

test _b[c.bmxbmi@0bn.MJ] = _b[c.bmxbmi@1.MJ] = _b[c.bmxbmi@2.MJ] = _b[c.bmxbmi@3.MJ] = _b[c.bmxbmi@4.MJ]
```

## Healthy Eating Index

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): mean hei2015,over(MJ)coeflegend
# svy, subpop(if include==1): mean hei2015,over(MJ)

test _b[c.hei2015@0bn.MJ] = _b[c.hei2015@1.MJ] = _b[c.hei2015@2.MJ] = _b[c.hei2015@3.MJ] = _b[c.hei2015@4.MJ]
```

# Associations between outcome (HTN category) & covariates

## MJ Category

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta MJ BP_cat,col percent
```

## Gender

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta gndr BP_cat,col percent
```

## Education

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta EDUC_cat BP_cat,col percent
```

## Race

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta race_eth BP_cat,col percent
```

## Survey Year

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta sddsrvyr BP_cat,col percent
```

## Income

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): mean indfmpir,over(BP_cat)coeflegend
# svy, subpop(if include==1): mean indfmpir,over(BP_cat)

test _b[c.indfmpir@0bn.BP_cat] = _b[c.indfmpir@1.BP_cat] = _b[c.indfmpir@2.BP_cat] = _b[c.indfmpir@3.BP_cat]
```

## Age

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): mean ridageyr,over(BP_cat)coeflegend
# svy, subpop(if include==1): mean ridageyr,over(BP_cat)

test _b[c.ridageyr@0bn.BP_cat] = _b[c.ridageyr@1.BP_cat] = _b[c.ridageyr@2.BP_cat] = _b[c.ridageyr@3.BP_cat]
```

## Smoking

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta SMK_cat BP_cat,col percent
```

## Alcohol

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): ta AL_cat BP_cat,col percent
```

## BMI

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): mean bmxbmi,over(BP_cat)coeflegend
# svy, subpop(if include==1): mean bmxbmi,over(BP_cat)

test _b[c.bmxbmi@0bn.BP_cat] = _b[c.bmxbmi@1.BP_cat] = _b[c.bmxbmi@2.BP_cat] = _b[c.bmxbmi@3.BP_cat]
```

## Healthy Eating Index

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

svy, subpop(if include==1): mean hei2015,over(BP_cat)coeflegend
# svy, subpop(if include==1): mean hei2015,over(BP_cat)

test _b[c.hei2015@0bn.BP_cat] = _b[c.hei2015@1.BP_cat] = _b[c.hei2015@2.BP_cat] = _b[c.hei2015@3.BP_cat]
```

# Crude coefficients and ORs

## Coefficients

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ
```

## ORs

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ,or
```

# Correlations among potential confounders






