---
title: "DAG"
author: "Matthew Hoctor, Bryon Langford"
date: "6/24/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(dplyr)
#library(readxl)
#library(tidyverse)
#library(ggplot2)
#library(CarletonStats)
#library(pwr)
#library(BSDA)
#library(exact2x2)
#library(car)
#library(dvmisc)
#library(emmeans)
#library(gridExtra)
#library(DescTools)
#library(epitools)
#library(pROC)
#library(rje)
#library(lmtest)
#library(gtsummary)
#library(mfp)
#library(linearspline)
library(dagitty)
```

# Preliminary DAG

This DAG is based on Vidot et al.'s causal scheme [link](https://pubmed.ncbi.nlm.nih.gov/31439096/):

```{r Vidot DAG}
g0 <- dagitty("dag {
Survey_Year -> Cannabis
Survey_Year -> Hypertension
Age -> Cannabis
Age -> Hypertension
Alcohol -> Hypertension
BMI -> Hypertension
Cannabis -> Alcohol
Cannabis -> BMI
Cannabis -> Hypertension
Cannabis -> Tobacco
Education -> Cannabis
Education -> Hypertension
Gender -> Cannabis
Gender -> Hypertension
Race -> Cannabis
Race -> Hypertension
Tobacco -> Hypertension
}
")

coordinates(g0) <- 
  list(
    x=c(Cannabis=0,
        Alcohol=1,Tobacco=1,BMI=1,Gender=1,Age=1,Race=1,Survey_Year=1,Education=1,
        Hypertension=2),
    y=c(Alcohol=0,Tobacco=1,BMI=2,
        Cannabis=3,
        Hypertension=3,
        Gender=4,Age=5,Race=6,Survey_Year=7,Education=8)
  )

plot(g0)
```

## Code for Daggity.net

dag {
bb="0,0,1,1"
"Survey Year" [adjusted,pos="0.340,0.791"]
Age [adjusted,pos="0.336,0.573"]
Alcohol [pos="0.355,0.105"]
BMI [pos="0.347,0.313"]
Cannabis [exposure,pos="0.169,0.401"]
Gender [adjusted,pos="0.336,0.466"]
Hypertension [outcome,pos="0.554,0.402"]
Race [adjusted,pos="0.340,0.685"]
Tobacco [pos="0.344,0.209"]
"Survey Year" -> Cannabis
"Survey Year" -> Hypertension
Age -> Cannabis
Age -> Hypertension
Alcohol -> Hypertension
BMI -> Hypertension
Cannabis -> Alcohol
Cannabis -> BMI
Cannabis -> Hypertension
Cannabis -> Tobacco
Gender -> Cannabis
Gender -> Hypertension
Race -> Cannabis
Race -> Hypertension
Tobacco -> Hypertension
}

# Diet as a mediator

```{r diet DAG}
g1 <- dagitty("dag {
Survey_Year -> Cannabis
Survey_Year -> Hypertension
Age -> Cannabis
Age -> Hypertension
Alcohol -> Hypertension
BMI -> Hypertension
Cannabis -> Alcohol
Cannabis -> BMI
Cannabis -> Diet
Cannabis -> Hypertension
Cannabis -> Tobacco
Diet -> BMI
Diet -> Hypertension
Education -> Cannabis
Education -> Hypertension
Gender -> Cannabis
Gender -> Hypertension
Race -> Cannabis
Race -> Hypertension
Tobacco -> Hypertension
}
")

coordinates(g1) <- 
  list(
    x=c(Cannabis=0,
        Diet=0.66,
        Alcohol=1,Tobacco=1,Gender=1,Age=1,Race=1,Survey_Year=1,Education=1,
        BMI=1.33,
        Hypertension=2),
    y=c(Alcohol=0,Tobacco=1,
        Diet=2,BMI=2,
        Cannabis=3,
        Hypertension=3,
        Gender=4,Age=5,Race=6,Survey_Year=7,Education=8)
  )

plot(g1)
```
