---
title: "Dataset"
author: "Bryon Langford, Matthew Hoctor"
date: "6/30/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (Sys.info()["sysname"] == "Windows") 
  knitr::opts_chunk$set(engine.path = list(stata = "C:/Program Files/Stata17/StataBE-64")) 
if (!(Sys.info()["sysname"] == "Windows"))
  knitr::opts_chunk$set(engine.path = list(stata = "/Applications/Stata"))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

# 1 Import XPTs for 2007-2008

## Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2007-2008/DEMO_E.XPT"
save "temp/2007-2008/DEMO_E.dta",replace
de
clear
```

## Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2007-2008/DUQ_E.XPT"
save "temp/2007-2008/DUQ_E.dta",replace
de
clear
```

## Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2007-2008/BPX_E.XPT"
save "temp/2007-2008/BPX_E.dta",replace
de
clear
```

## Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2007-2008/BMX_E.XPT"
save "temp/2007-2008/BMX_E.dta",replace
de
clear
```

## Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2007-2008/SMQ_E.XPT"
save "temp/2007-2008/SMQ_E.dta",replace
de
clear
```

## Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2007-2008/ALQ_E.XPT"
save "temp/2007-2008/ALQ_E.dta",replace
de
clear
```

## Merge Files

```{stata}
# use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_DEMO_E.dta", clear
# save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta",replace
# merge 1:1 seqn using "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_BMX_E.dta"
# rename _merge Merge_BM
# tab Merge_BM
# duplicates report seqn
# save,replace
```

# 2 Import XPTs for 2009-2010

## Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2009-2010/DEMO_F.XPT"
save "temp/2009-2010/DEMO_F.dta",replace
de
clear
```

## Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2009-2010/DUQ_F.XPT"
save "temp/2009-2010/DUQ_F.dta",replace
de
clear
```

## Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2009-2010/BPX_F.XPT"
save "temp/2009-2010/BPX_F.dta",replace
de
clear
```

## Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2009-2010/BMX_F.XPT"
save "temp/2009-2010/BMX_F.dta",replace
de
clear
```

## Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2009-2010/SMQ_F.XPT"
save "temp/2009-2010/SMQ_F.dta",replace
de
clear
```

## Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2009-2010/ALQ_F.XPT"
save "temp/2009-2010/ALQ_F.dta",replace
de
clear
```

## Merge Files

```{stata}
# use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_DEMO_F.dta", clear
# save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta",replace
# merge 1:1 seqn using "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_BMX_F.dta"
# rename _merge Merge_BM
# tab Merge_BM
# duplicates report seqn
# save,replace
```

# 3 Import XPTs for 2011-2012

## Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2011-2012/DEMO_G.XPT"
save "temp/2011-2012/DEMO_G.dta",replace
de
clear
```

## Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2011-2012/DUQ_G.XPT"
save "temp/2011-2012/DUQ_G.dta",replace
de
clear
```

## Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2011-2012/BPX_G.XPT"
save "temp/2011-2012/BPX_G.dta",replace
de
clear
```

## Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2011-2012/BMX_G.XPT"
save "temp/2011-2012/BMX_G.dta",replace
de
clear
```

## Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2011-2012/SMQ_G.XPT"
save "temp/2011-2012/SMQ_G.dta",replace
de
clear
```

## Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2011-2012/ALQ_G.XPT"
save "temp/2011-2012/ALQ_G.dta",replace
de
clear
```

## Merge Files

```{stata}
# use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_DEMO_G.dta", clear
# save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta",replace
# merge 1:1 seqn using "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_BMX_G.dta"
# rename _merge Merge_BM
# tab Merge_BM
# duplicates report seqn
# save,replace
```

# 4 Import XPTs for 2013-2014

## Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2013-2014/DEMO_H.XPT"
save "temp/2013-2014/DEMO_H.dta",replace
de
clear
```

## Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2013-2014/DUQ_H.XPT"
save "temp/2013-2014/DUQ_H.dta",replace
de
clear
```

## Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2013-2014/BPX_H.XPT"
save "temp/2013-2014/BPX_H.dta",replace
de
clear
```

## Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2013-2014/BMX_H.XPT"
save "temp/2013-2014/BMX_H.dta",replace
de
clear
```

## Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2013-2014/SMQ_H.XPT"
save "temp/2013-2014/SMQ_H.dta",replace
de
clear
```

## Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2013-2014/ALQ_H.XPT"
save "temp/2013-2014/ALQ_H.dta",replace
de
clear
```

## Merge Files

```{stata}
# use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_DEMO_H.dta", clear
# save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta",replace
# merge 1:1 seqn using "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_BMX_H.dta"
# rename _merge Merge_BM
# tab Merge_BM
# duplicates report seqn
# save,replace
```

# 5 Import XPTs for 2015-2016

## Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2015-2016/DEMO_I.XPT"
save "temp/2015-2016/DEMO_I.dta",replace
de
clear
```

## Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2015-2016/DUQ_I.XPT"
save "temp/2015-2016/DUQ_I.dta",replace
de
clear
```

## Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2015-2016/BPX_I.XPT"
save "temp/2015-2016/BPX_I.dta",replace
de
clear
```

## Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2015-2016/BMX_I.XPT"
save "temp/2015-2016/BMX_I.dta",replace
de
clear
```

## Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2015-2016/SMQ_I.XPT"
save "temp/2015-2016/SMQ_I.dta",replace
de
clear
```

## Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2015-2016/ALQ_I.XPT"
save "temp/2015-2016/ALQ_I.dta",replace
de
clear
```

## Merge Files

```{stata}
# use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_DEMO_I.dta", clear
# save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta",replace
# merge 1:1 seqn using "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_BMX_I.dta"
# rename _merge Merge_BM
# tab Merge_BM
# duplicates report seqn
# save,replace
```

# 6 Import XPTs for 2017-2018

## Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2017-2018/DEMO_J.XPT"
save "temp/2017-2018/DEMO_J.dta",replace
de
clear
```

## Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2017-2018/DUQ_J.XPT"
save "temp/2017-2018/DUQ_J.dta",replace
de
clear
```

## Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2017-2018/BPX_J.XPT"
save "temp/2017-2018/BPX_J.dta",replace
de
clear
```

## Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2017-2018/BMX_J.XPT"
save "temp/2017-2018/BMX_J.dta",replace
de
clear
```

## Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2017-2018/SMQ_J.XPT"
save "temp/2017-2018/SMQ_J.dta",replace
de
clear
```

## Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2017-2018/ALQ_J.XPT"
save "temp/2017-2018/ALQ_J.dta",replace
de
clear
```

## Merge Files

```{stata}
# use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_DEMO_J.dta", clear
# save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta",replace
# merge 1:1 seqn using "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_BMX_J.dta"
# rename _merge Merge_BM
# tab Merge_BM
# duplicates report seqn
# save,replace
```



