---
title: "Data Download"
author: "Bryon Langford, Matthew Hoctor"
date: "6/30/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(engine.path = list(
  stata = "C:/Program Files/Stata17/StataBE-64",
  stata = "/Applications/Stata"
))
```

```{r libraries, include=FALSE}
#library(Statamarkdown)
```

# 2007-2008

Please note that FPED & DR1IFF data sets have been compiled into HEI-2015 by Abigail Newby-Kew, and will not be downloaded.

```{r 2007-2008 downloads}
if(!file.exists("data/2007-2008/DEMO_E.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2007-2008/DEMO_E.XPT", 
                destfile = "data/2007-2008/DEMO_E.XPT",
                mode = "wb")
}
if(!file.exists("data/2007-2008/DUQ_E.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2007-2008/DUQ_E.XPT", 
                destfile = "data/2007-2008/DUQ_E.XPT",
                mode = "wb")
}
if(!file.exists("data/2007-2008/BPX_E.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2007-2008/BPX_E.XPT", 
                destfile = "data/2007-2008/BPX_E.XPT",
                mode = "wb")
}
# if(!file.exists("data/2007-2008/DR1IFF_E.XPT")){
#   download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2007-2008/DR1IFF_E.XPT", 
#                 destfile = "data/2007-2008/DR1IFF_E.XPT",
#                 mode = "wb")
# }
if(!file.exists("data/2007-2008/BMX_E.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2007-2008/BMX_E.XPT", 
                destfile = "data/2007-2008/BMX_E.XPT",
                mode = "wb")
}
if(!file.exists("data/2007-2008/SMQ_E.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2007-2008/SMQ_E.XPT", 
                destfile = "data/2007-2008/SMQ_E.XPT",
                mode = "wb")
}
if(!file.exists("data/2007-2008/ALQ_E.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2007-2008/ALQ_E.XPT", 
                destfile = "data/2007-2008/ALQ_E.XPT",
                mode = "wb")
}
if(!file.exists("data/2007-2008/DR1TOT_E.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2007-2008/DR1TOT_E.XPT", 
                destfile = "data/2007-2008/DR1TOT_E.XPT",
                mode = "wb")
}
if(!file.exists("data/2007-2008/DR2TOT_E.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2007-2008/DR2TOT_E.XPT", 
                destfile = "data/2007-2008/DR2TOT_E.XPT",
                mode = "wb")
}
```

# 2009-2010

Please note that FPED & DR1IFF data sets have been compiled into HEI-2015 by Abigail Newby-Kew, and will not be downloaded.

```{r 2009-2010 downloads}
if(!file.exists("data/2009-2010/DEMO_F.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2009-2010/DEMO_F.XPT", 
                destfile = "data/2009-2010/DEMO_F.XPT",
                mode = "wb")
}
if(!file.exists("data/2009-2010/DUQ_F.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2009-2010/DUQ_F.XPT", 
                destfile = "data/2009-2010/DUQ_F.XPT",
                mode = "wb")
}
if(!file.exists("data/2009-2010/BPX_F.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2009-2010/BPX_F.XPT", 
                destfile = "data/2009-2010/BPX_F.XPT",
                mode = "wb")
}
# if(!file.exists("data/2009-2010/DR1IFF_F.XPT")){
#   download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2009-2010/DR1IFF_F.XPT", 
#                 destfile = "data/2009-2010/DR1IFF_F.XPT",
#                 mode = "wb")
# }
if(!file.exists("data/2009-2010/BMX_F.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2009-2010/BMX_F.XPT", 
                destfile = "data/2009-2010/BMX_F.XPT",
                mode = "wb")
}
if(!file.exists("data/2009-2010/SMQ_F.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2009-2010/SMQ_F.XPT", 
                destfile = "data/2009-2010/SMQ_F.XPT",
                mode = "wb")
}
if(!file.exists("data/2009-2010/ALQ_F.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2009-2010/ALQ_F.XPT", 
                destfile = "data/2009-2010/ALQ_F.XPT",
                mode = "wb")
}
if(!file.exists("data/2009-2010/DR1TOT_F.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2009-2010/DR1TOT_F.XPT", 
                destfile = "data/2009-2010/DR1TOT_F.XPT",
                mode = "wb")
}
if(!file.exists("data/2009-2010/DR2TOT_F.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2009-2010/DR2TOT_F.XPT", 
                destfile = "data/2009-2010/DR2TOT_F.XPT",
                mode = "wb")
}
```

# 2011-2012

Please note that FPED & DR1IFF data sets have been compiled into HEI-2015 by Abigail Newby-Kew, and will not be downloaded.

```{r 2011-2012 downloads}
if(!file.exists("data/2011-2012/DEMO_G.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/DEMO_G.XPT", 
                destfile = "data/2011-2012/DEMO_G.XPT",
                mode = "wb")
}
if(!file.exists("data/2011-2012/DUQ_G.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/DUQ_G.XPT", 
                destfile = "data/2011-2012/DUQ_G.XPT",
                mode = "wb")
}
if(!file.exists("data/2011-2012/BPX_G.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/BPX_G.XPT", 
                destfile = "data/2011-2012/BPX_G.XPT",
                mode = "wb")
}
# if(!file.exists("data/2011-2012/DR1IFF_G.XPT")){
#   download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/DR1IFF_G.XPT", 
#                 destfile = "data/2011-2012/DR1IFF_G.XPT",
#                 mode = "wb")
# }
if(!file.exists("data/2011-2012/BMX_G.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/BMX_G.XPT", 
                destfile = "data/2011-2012/BMX_G.XPT",
                mode = "wb")
}
if(!file.exists("data/2011-2012/SMQ_G.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/SMQ_G.XPT", 
                destfile = "data/2011-2012/SMQ_G.XPT",
                mode = "wb")
}
if(!file.exists("data/2011-2012/ALQ_G.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/ALQ_G.XPT", 
                destfile = "data/2011-2012/ALQ_G.XPT",
                mode = "wb")
}
if(!file.exists("data/2011-2012/DR1TOT_G.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/DR1TOT_G.XPT", 
                destfile = "data/2011-2012/DR1TOT_G.XPT",
                mode = "wb")
}
if(!file.exists("data/2011-2012/DR2TOT_G.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2011-2012/DR2TOT_G.XPT", 
                destfile = "data/2011-2012/DR2TOT_G.XPT",
                mode = "wb")
}
```

# 2013-2014

Please note that FPED & DR1IFF data sets have been compiled into HEI-2015 by Abigail Newby-Kew, and will not be downloaded.

```{r 2013-2014 downloads}
if(!file.exists("data/2013-2014/DEMO_H.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/DEMO_H.XPT", 
                destfile = "data/2013-2014/DEMO_H.XPT",
                mode = "wb")
}
if(!file.exists("data/2013-2014/DUQ_H.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/DUQ_H.XPT", 
                destfile = "data/2013-2014/DUQ_H.XPT",
                mode = "wb")
}
if(!file.exists("data/2013-2014/BPX_H.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/BPX_H.XPT", 
                destfile = "data/2013-2014/BPX_H.XPT",
                mode = "wb")
}
# if(!file.exists("data/2013-2014/DR1IFF_H.XPT")){
#   download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/DR1IFF_H.XPT", 
#                 destfile = "data/2013-2014/DR1IFF_H.XPT",
#                 mode = "wb")
# }
if(!file.exists("data/2013-2014/BMX_H.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/BMX_H.XPT", 
                destfile = "data/2013-2014/BMX_H.XPT",
                mode = "wb")
}
if(!file.exists("data/2013-2014/SMQ_H.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/SMQ_H.XPT", 
                destfile = "data/2013-2014/SMQ_H.XPT",
                mode = "wb")
}
if(!file.exists("data/2013-2014/ALQ_H.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/ALQ_H.XPT", 
                destfile = "data/2013-2014/ALQ_H.XPT",
                mode = "wb")
}
if(!file.exists("data/2013-2014/DR1TOT_H.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/DR1TOT_H.XPT", 
                destfile = "data/2013-2014/DR1TOT_H.XPT",
                mode = "wb")
}
if(!file.exists("data/2013-2014/DR2TOT_H.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2013-2014/DR2TOT_H.XPT", 
                destfile = "data/2013-2014/DR2TOT_H.XPT",
                mode = "wb")
}
```

# 2015-2016

Please note that FPED & DR1IFF data sets have been compiled into HEI-2015 by Abigail Newby-Kew, and will not be downloaded.

```{r 2015-2016 downloads}
if(!file.exists("data/2015-2016/DEMO_I.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/DEMO_I.XPT", 
                destfile = "data/2015-2016/DEMO_I.XPT",
               mode = "wb")
}
if(!file.exists("data/2015-2016/DUQ_I.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/DUQ_I.XPT", 
                destfile = "data/2015-2016/DUQ_I.XPT",
               mode = "wb")
}
if(!file.exists("data/2015-2016/BPX_I.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/BPX_I.XPT", 
                destfile = "data/2015-2016/BPX_I.XPT",
               mode = "wb")
}
# if(!file.exists("data/2015-2016/DR1IFF_I.XPT")){
#   download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/DR1IFF_I.XPT", 
#                 destfile = "data/2015-2016/DR1IFF_I.XPT",
#                mode = "wb")
# }
if(!file.exists("data/2015-2016/BMX_I.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/BMX_I.XPT", 
                destfile = "data/2015-2016/BMX_I.XPT",
               mode = "wb")
}
if(!file.exists("data/2015-2016/SMQ_I.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/SMQ_I.XPT", 
                destfile = "data/2015-2016/SMQ_I.XPT",
               mode = "wb")
}
if(!file.exists("data/2015-2016/ALQ_I.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/ALQ_I.XPT", 
                destfile = "data/2015-2016/ALQ_I.XPT",
               mode = "wb")
}
if(!file.exists("data/2015-2016/DR1TOT_I.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/DR1TOT_I.XPT", 
                destfile = "data/2015-2016/DR1TOT_I.XPT",
                mode = "wb")
}
if(!file.exists("data/2015-2016/DR2TOT_I.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2015-2016/DR2TOT_I.XPT", 
                destfile = "data/2015-2016/DR2TOT_I.XPT",
                mode = "wb")
}
```

# 2017-2018

Please note that FPED & DR1IFF data sets have been compiled into HEI-2015 by Abigail Newby-Kew, and will not be downloaded.

```{r 2017-2018 downloads}
if(!file.exists("data/2017-2018/DEMO_J.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/DEMO_J.XPT", 
                destfile = "data/2017-2018/DEMO_J.XPT",
               mode = "wb")
}
if(!file.exists("data/2017-2018/DUQ_J.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/DUQ_J.XPT", 
                destfile = "data/2017-2018/DUQ_J.XPT",
               mode = "wb")
}
if(!file.exists("data/2017-2018/BPX_J.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/BPX_J.XPT", 
                destfile = "data/2017-2018/BPX_J.XPT",
               mode = "wb")
}
# if(!file.exists("data/2017-2018/DR1IFF_J.XPT")){
#   download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/DR1IFF_J.XPT", 
#                 destfile = "data/2017-2018/DR1IFF_J.XPT",
#                mode = "wb")
# }
if(!file.exists("data/2017-2018/BMX_J.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/BMX_J.XPT", 
                destfile = "data/2017-2018/BMX_J.XPT",
               mode = "wb")
}
if(!file.exists("data/2017-2018/SMQ_J.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/SMQ_J.XPT", 
                destfile = "data/2017-2018/SMQ_J.XPT",
               mode = "wb")
}
if(!file.exists("data/2017-2018/ALQ_J.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/ALQ_J.XPT", 
                destfile = "data/2017-2018/ALQ_J.XPT",
               mode = "wb")
}
if(!file.exists("data/2017-2018/DR1TOT_J.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/DR1TOT_J.XPT", 
                destfile = "data/2017-2018/DR1TOT_J.XPT",
                mode = "wb")
}
if(!file.exists("data/2017-2018/DR2TOT_J.XPT")){
  download.file("https://wwwn.cdc.gov/Nchs/Nhanes/2017-2018/DR2TOT_J.XPT", 
                destfile = "data/2017-2018/DR2TOT_J.XPT",
                mode = "wb")
}
```
