---
title: "Dataset"
author: "Bryon Langford, Matthew Hoctor"
date: "6/30/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(engine.path = list(
  stata = "C:/Program Files/Stata17/StataBE-64"
))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

# 1 Downloading data from the NHANES website

# 2 Import Sociodemographic XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\DEMO_E.XPT"
save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_DEMO_E.dta",replace
de
clear
```

# 3 Import Body Measures XPT

## a

The following STATA chunk imports and describes the body measures NHANES dataset:

```{stata}
import sasxport5 "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\BMX_E.XPT"
save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_BMX_E.dta",replace
de
clear
```

## b

The following STATA chunk imports the body measures NHANES dataset, keeps only the needed variables, saves and describes the resulting data subset:

```{stata}
import sasxport5 "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\BMX_E.XPT"
keep seqn bmdstats bm*wt bm*ht bmxbmi bm*waist
save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_BMX_E.dta",replace
de
clear
```

## c import diet behaviour and nutrition

```{stata}
import sasxport5 "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\DBQ_E.XPT"
keep seqn dbq360 dbd381 dbq400 dbd411 dbq421
save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_DBQ_E.dta",replace
de
clear
```

## d import health insurance

```{stata}
import sasxport5 "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\HIQ_E.XPT"
keep seqn hiq011 hiq031a  hiq031b hiq031c hiq031d hiq031e hiq031f hiq031g hiq031h hiq031i hiq031j hiq031aa
save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_HIQ_E.dta",replace
de
clear
```

# 4 Import Food Security XPT

## a

The following STATA chunk imports and describes the Food Security NHANES dataset:

```{stata}
import sasxport5 "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\FSQ_E.XPT"
#save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_FSQ_E.dta",replace
de
clear
```

## b

The following STATA chunk imports the food security NHANES dataset, keeps only the needed variables, saves and describes the resulting data subset:

```{stata}
import sasxport5 "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\FSQ_E.XPT"
keep seqn fsdch
save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_FSQ_E.dta",replace
de
clear
```

# 5 Merge files

## c demographics and body measurement files

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_DEMO_E.dta", clear
save "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta",replace
merge 1:1 seqn using "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_BMX_E.dta"
rename _merge Merge_BM
tab Merge_BM
duplicates report seqn
save,replace
```

## d merge food security data into main dataset

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta", clear
merge 1:1 seqn using "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_FSQ_E.dta"
rename _merge Merge_FS
tab Merge_FS
duplicates report seqn
save,replace
```

# 6 Merge additional datasets

## a merge diet & nutrition data into main dataset

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta", clear
merge 1:1 seqn using "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_DBQ_E.dta"
rename _merge Merge_DB
tab Merge_DB
duplicates report seqn
save,replace
```

## b merge health insurance data into main dataset

```{stata}
use "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\NHANES0708_merged.dta", clear
merge 1:1 seqn using "C:\Users\Matt\Documents\EPI536\EPI536-Assignments\temp_HIQ_E.dta"
rename _merge Merge_HI
tab Merge_HI
duplicates report seqn
save,replace
```

