---
title: "Dataset"
author: "Bryon Langford, Matthew Hoctor"
date: "6/30/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (Sys.info()["sysname"] == "Windows") 
  knitr::opts_chunk$set(engine.path = list(stata = "C:/Program Files/Stata17/StataBE-64")) 
if ((Sys.info()["sysname"] == "Darwin"))
  knitr::opts_chunk$set(engine.path = list(stata = "/Applications/Stata/StataIC"))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

# Import Files

## 0 Import XPTs for 2005-2006

### Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2005-2006/DEMO_D.XPT"
save "temp/2005-2006/DEMO_D.dta",replace
de
clear
```

### Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2005-2006/DUQ_D.XPT"
keep seqn duq200 duq220q duq220u duq230 duq210
save "temp/2005-2006/DUQ_D.dta",replace
de
clear
```

### Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2005-2006/BPX_D.XPT"
keep seqn bpxsy1 bpxsy2 bpxsy3 bpxsy4 bpxdi1 bpxdi2 bpxdi3 bpxdi4
save "temp/2005-2006/BPX_D.dta",replace
de
clear
```

### Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2005-2006/BMX_D.XPT"
keep seqn bmxwt bmxbmi bmxht bmxwaist
save "temp/2005-2006/BMX_D.dta",replace
de
clear
```

### Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2005-2006/SMQ_D.XPT"
keep seqn smq020 smq040 smd650
save "temp/2005-2006/SMQ_D.dta",replace
de
clear
```

### Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2005-2006/ALQ_D.XPT"
keep seqn alq101 alq130
save "temp/2005-2006/ALQ_D.dta",replace
de
clear
```

### Day 1 Nutrition, DR1TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2005-2006/DR1TOT_D.XPT"
keep seqn dr1tkcal
save "temp/2005-2006/DR1TOT_D.dta",replace
de
clear
```

### Day 2 Nutrition, DR2TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2005-2006/DR2TOT_D.XPT"
keep seqn dr2tkcal
save "temp/2005-2006/DR2TOT_D.dta",replace
de
clear
```

## 1 Import XPTs for 2007-2008

### Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2007-2008/DEMO_E.XPT"
save "temp/2007-2008/DEMO_E.dta",replace
de
clear
```

### Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2007-2008/DUQ_E.XPT"
keep seqn duq200 duq220q duq220u duq230 duq210
save "temp/2007-2008/DUQ_E.dta",replace
de
clear
```

### Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2007-2008/BPX_E.XPT"
keep seqn bpxsy1 bpxsy2 bpxsy3 bpxsy4 bpxdi1 bpxdi2 bpxdi3 bpxdi4
save "temp/2007-2008/BPX_E.dta",replace
de
clear
```

### Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2007-2008/BMX_E.XPT"
keep seqn bmxwt bmxbmi bmxht bmxwaist
save "temp/2007-2008/BMX_E.dta",replace
de
clear
```

### Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2007-2008/SMQ_E.XPT"
keep seqn smq020 smq040 smd650
save "temp/2007-2008/SMQ_E.dta",replace
de
clear
```

### Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2007-2008/ALQ_E.XPT"
keep seqn alq101 alq130
save "temp/2007-2008/ALQ_E.dta",replace
de
clear
```

### Day 1 Nutrition, DR1TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2007-2008/DR1TOT_E.XPT"
keep seqn dr1tkcal
save "temp/2007-2008/DR1TOT_E.dta",replace
de
clear
```

### Day 2 Nutrition, DR2TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2007-2008/DR2TOT_E.XPT"
keep seqn dr2tkcal
save "temp/2007-2008/DR2TOT_E.dta",replace
de
clear
```

## 2 Import XPTs for 2009-2010

### Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2009-2010/DEMO_F.XPT"
save "temp/2009-2010/DEMO_F.dta",replace
de
clear
```

### Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2009-2010/DUQ_F.XPT"
keep seqn duq200 duq220q duq220u duq230 duq210
save "temp/2009-2010/DUQ_F.dta",replace
de
clear
```

### Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2009-2010/BPX_F.XPT"
keep seqn bpxsy1 bpxsy2 bpxsy3 bpxsy4 bpxdi1 bpxdi2 bpxdi3 bpxdi4
save "temp/2009-2010/BPX_F.dta",replace
de
clear
```

### Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2009-2010/BMX_F.XPT"
keep seqn bmxwt bmxbmi bmxht bmxwaist
save "temp/2009-2010/BMX_F.dta",replace
de
clear
```

### Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2009-2010/SMQ_F.XPT"
keep seqn smq020 smq040 smd650
save "temp/2009-2010/SMQ_F.dta",replace
de
clear
```

### Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2009-2010/ALQ_F.XPT"
keep seqn alq101 alq130
save "temp/2009-2010/ALQ_F.dta",replace
de
clear
```

### Day 1 Nutrition, DR1TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2009-2010/DR1TOT_F.XPT"
keep seqn dr1tkcal
save "temp/2009-2010/DR1TOT_F.dta",replace
de
clear
```

### Day 2 Nutrition, DR2TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2009-2010/DR2TOT_F.XPT"
keep seqn dr2tkcal
save "temp/2009-2010/DR2TOT_F.dta",replace
de
clear
```

## 3 Import XPTs for 2011-2012

### Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2011-2012/DEMO_G.XPT"
save "temp/2011-2012/DEMO_G.dta",replace
de
clear
```

### Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2011-2012/DUQ_G.XPT"
keep seqn duq200 duq220q duq220u duq230 duq210
save "temp/2011-2012/DUQ_G.dta",replace
de
clear
```

### Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2011-2012/BPX_G.XPT"
keep seqn bpxsy1 bpxsy2 bpxsy3 bpxsy4 bpxdi1 bpxdi2 bpxdi3 bpxdi4
save "temp/2011-2012/BPX_G.dta",replace
de
clear
```

### Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2011-2012/BMX_G.XPT"
keep seqn bmxwt bmxbmi bmxht bmxwaist
save "temp/2011-2012/BMX_G.dta",replace
de
clear
```

### Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2011-2012/SMQ_G.XPT"
keep seqn smq020 smq040 smd650
save "temp/2011-2012/SMQ_G.dta",replace
de
clear
```

### Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2011-2012/ALQ_G.XPT"
keep seqn alq101 alq130
save "temp/2011-2012/ALQ_G.dta",replace
de
clear
```

### Day 1 Nutrition, DR1TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2011-2012/DR1TOT_G.XPT"
keep seqn dr1tkcal
save "temp/2011-2012/DR1TOT_G.dta",replace
de
clear
```

### Day 2 Nutrition, DR2TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2011-2012/DR2TOT_G.XPT"
keep seqn dr2tkcal
save "temp/2011-2012/DR2TOT_G.dta",replace
de
clear
```

## 4 Import XPTs for 2013-2014

### Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2013-2014/DEMO_H.XPT"
save "temp/2013-2014/DEMO_H.dta",replace
de
clear
```

### Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2013-2014/DUQ_H.XPT"
keep seqn duq200 duq220q duq220u duq230 duq210
save "temp/2013-2014/DUQ_H.dta",replace
de
clear
```

### Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2013-2014/BPX_H.XPT"
keep seqn bpxsy1 bpxsy2 bpxsy3 bpxsy4 bpxdi1 bpxdi2 bpxdi3 bpxdi4
save "temp/2013-2014/BPX_H.dta",replace
de
clear
```

### Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2013-2014/BMX_H.XPT"
keep seqn bmxwt bmxbmi bmxht bmxwaist
save "temp/2013-2014/BMX_H.dta",replace
de
clear
```

### Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2013-2014/SMQ_H.XPT"
keep seqn smq020 smq040 smd650
save "temp/2013-2014/SMQ_H.dta",replace
de
clear
```

### Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2013-2014/ALQ_H.XPT"
keep seqn alq101 alq130
save "temp/2013-2014/ALQ_H.dta",replace
de
clear
```

### Day 1 Nutrition, DR1TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2013-2014/DR1TOT_H.XPT"
keep seqn dr1tkcal
save "temp/2013-2014/DR1TOT_H.dta",replace
de
clear
```

### Day 2 Nutrition, DR2TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2013-2014/DR2TOT_H.XPT"
keep seqn dr2tkcal
save "temp/2013-2014/DR2TOT_H.dta",replace
de
clear
```

## 5 Import XPTs for 2015-2016

### Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2015-2016/DEMO_I.XPT"
save "temp/2015-2016/DEMO_I.dta",replace
de
clear
```

### Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2015-2016/DUQ_I.XPT"
keep seqn duq200 duq220q duq220u duq230 duq210
save "temp/2015-2016/DUQ_I.dta",replace
de
clear
```

### Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2015-2016/BPX_I.XPT"
keep seqn bpxsy1 bpxsy2 bpxsy3 bpxsy4 bpxdi1 bpxdi2 bpxdi3 bpxdi4
save "temp/2015-2016/BPX_I.dta",replace
de
clear
```

### Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2015-2016/BMX_I.XPT"
keep seqn bmxwt bmxbmi bmxht bmxwaist
save "temp/2015-2016/BMX_I.dta",replace
de
clear
```

### Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2015-2016/SMQ_I.XPT"
keep seqn smq020 smq040 smd650
save "temp/2015-2016/SMQ_I.dta",replace
de
clear
```

### Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2015-2016/ALQ_I.XPT"
keep seqn alq101 alq130
save "temp/2015-2016/ALQ_I.dta",replace
de
clear
```

### Day 1 Nutrition, DR1TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2015-2016/DR1TOT_I.XPT"
keep seqn dr1tkcal
save "temp/2015-2016/DR1TOT_I.dta",replace
de
clear
```

### Day 2 Nutrition, DR2TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2015-2016/DR2TOT_I.XPT"
keep seqn dr2tkcal
save "temp/2015-2016/DR2TOT_I.dta",replace
de
clear
```

## 6 Import XPTs for 2017-2018

### Demographics, DEMO_XYZ.XPT

The following STATA chunk imports and describes the sociodemographic NHANES dataset:

```{stata}
import sasxport5 "data/2017-2018/DEMO_J.XPT"
save "temp/2017-2018/DEMO_J.dta",replace
de
clear
```

### Drug Use, DUQ_XYZ.XPT

```{stata}
import sasxport5 "data/2017-2018/DUQ_J.XPT"
keep seqn duq200 duq220q duq220u duq230 duq210
save "temp/2017-2018/DUQ_J.dta",replace
de
clear
```

### Blood Pressure, BPX_XYZ.XPT

```{stata}
import sasxport5 "data/2017-2018/BPX_J.XPT"
keep seqn bpxsy1 bpxsy2 bpxsy3 bpxsy4 bpxdi1 bpxdi2 bpxdi3 bpxdi4
save "temp/2017-2018/BPX_J.dta",replace
de
clear
```

### Body Measurements, BMX_XYZ.XPT

```{stata}
import sasxport5 "data/2017-2018/BMX_J.XPT"
keep seqn bmxwt bmxbmi bmxht bmxwaist
save "temp/2017-2018/BMX_J.dta",replace
de
clear
```

### Smoking, SMQ_XYZ.XPT

```{stata}
import sasxport5 "data/2017-2018/SMQ_J.XPT"
keep seqn smq020 smq040 smd650
save "temp/2017-2018/SMQ_J.dta",replace
de
clear
```

### Alcohol, ALQ_XYZ.XPT

```{stata}
import sasxport5 "data/2017-2018/ALQ_J.XPT"
keep seqn alq111 alq121 alq130
save "temp/2017-2018/ALQ_J.dta",replace
de
clear
```

### Day 1 Nutrition, DR1TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2017-2018/DR1TOT_J.XPT"
keep seqn dr1tkcal
save "temp/2017-2018/DR1TOT_J.dta",replace
de
clear
```

### Day 2 Nutrition, DR2TOT_XYZ.XPT

```{stata}
import sasxport5 "data/2017-2018/DR2TOT_J.XPT"
keep seqn dr2tkcal
save "temp/2017-2018/DR2TOT_J.dta",replace
de
clear
```

# Merge Files

## 2005-2006

Starting with the demographics file.

### BMX merge

```{stata}
use "temp\2005-2006\DEMO_D.dta", clear
save "data\NHANES0506_merged.dta",replace
merge 1:1 seqn using "temp\2005-2006\BMX_D.dta"
rename _merge Merge_BM
tab Merge_BM
duplicates report seqn
save,replace
```

### ALQ merge

```{stata}
use "data\NHANES0506_merged.dta", clear
merge 1:1 seqn using "temp\2005-2006\ALQ_D.dta"
rename _merge Merge_AL
tab Merge_AL
duplicates report seqn
save,replace
```

### BPX merge

```{stata}
use "data\NHANES0506_merged.dta", clear
merge 1:1 seqn using "temp\2005-2006\BPX_D.dta"
rename _merge Merge_BP
tab Merge_BP
duplicates report seqn
save,replace
```

### DUQ merge

```{stata}
use "data\NHANES0506_merged.dta", clear
merge 1:1 seqn using "temp\2005-2006\DUQ_D.dta"
rename _merge Merge_DU
tab Merge_DU
duplicates report seqn
save,replace
```

### SMQ merge

```{stata}
use "data\NHANES0506_merged.dta", clear
merge 1:1 seqn using "temp\2005-2006\SMQ_D.dta"
rename _merge Merge_SM
tab Merge_SM
duplicates report seqn
save,replace
```

### DR1TOT merge

```{stata}
use "data\NHANES0506_merged.dta", clear
merge 1:1 seqn using "temp\2005-2006\DR1TOT_D.dta"
rename _merge Merge_D1
tab Merge_D1
duplicates report seqn
save,replace
```

### DR2TOT merge

```{stata}
use "data\NHANES0506_merged.dta", clear
merge 1:1 seqn using "temp\2005-2006\DR2TOT_D.dta"
rename _merge Merge_D2
tab Merge_D2
duplicates report seqn
save,replace
```

## 2007-2008

Starting with the demographics file.

### BMX merge

```{stata}
use "temp\2007-2008\DEMO_E.dta", clear
save "data\NHANES0708_merged.dta",replace
merge 1:1 seqn using "temp\2007-2008\BMX_E.dta"
rename _merge Merge_BM
tab Merge_BM
duplicates report seqn
save,replace
```

### ALQ merge

```{stata}
use "data\NHANES0708_merged.dta", clear
merge 1:1 seqn using "temp\2007-2008\ALQ_E.dta"
rename _merge Merge_AL
tab Merge_AL
duplicates report seqn
save,replace
```

### BPX merge

```{stata}
use "data\NHANES0708_merged.dta", clear
merge 1:1 seqn using "temp\2007-2008\BPX_E.dta"
rename _merge Merge_BP
tab Merge_BP
duplicates report seqn
save,replace
```

### DUQ merge

```{stata}
use "data\NHANES0708_merged.dta", clear
merge 1:1 seqn using "temp\2007-2008\DUQ_E.dta"
rename _merge Merge_DU
tab Merge_DU
duplicates report seqn
save,replace
```

### SMQ merge

```{stata}
use "data\NHANES0708_merged.dta", clear
merge 1:1 seqn using "temp\2007-2008\SMQ_E.dta"
rename _merge Merge_SM
tab Merge_SM
duplicates report seqn
save,replace
```

### DR1TOT merge

```{stata}
use "data\NHANES0708_merged.dta", clear
merge 1:1 seqn using "temp\2007-2008\DR1TOT_E.dta"
rename _merge Merge_D1
tab Merge_D1
duplicates report seqn
save,replace
```

### DR2TOT merge

```{stata}
use "data\NHANES0708_merged.dta", clear
merge 1:1 seqn using "temp\2007-2008\DR2TOT_E.dta"
rename _merge Merge_D2
tab Merge_D2
duplicates report seqn
save,replace
```

## 2009-2010

Starting with the demographics file.

### BMX merge

```{stata}
use "temp\2009-2010\DEMO_F.dta", clear
save "data\NHANES0910_merged.dta",replace
merge 1:1 seqn using "temp\2009-2010\BMX_F.dta"
rename _merge Merge_BM
tab Merge_BM
duplicates report seqn
save,replace
```

### ALQ merge

```{stata}
use "data\NHANES0910_merged.dta", clear
merge 1:1 seqn using "temp\2009-2010\ALQ_F.dta"
rename _merge Merge_AL
tab Merge_AL
duplicates report seqn
save,replace
```

### BPX merge

```{stata}
use "data\NHANES0910_merged.dta", clear
merge 1:1 seqn using "temp\2009-2010\BPX_F.dta"
rename _merge Merge_BP
tab Merge_BP
duplicates report seqn
save,replace
```

### DUQ merge

```{stata}
use "data\NHANES0910_merged.dta", clear
merge 1:1 seqn using "temp\2009-2010\DUQ_F.dta"
rename _merge Merge_DU
tab Merge_DU
duplicates report seqn
save,replace
```

### SMQ merge

```{stata}
use "data\NHANES0910_merged.dta", clear
merge 1:1 seqn using "temp\2009-2010\SMQ_F.dta"
rename _merge Merge_SM
tab Merge_SM
duplicates report seqn
save,replace
```

### DR1TOT merge

```{stata}
use "data\NHANES0910_merged.dta", clear
merge 1:1 seqn using "temp\2009-2010\DR1TOT_F.dta"
rename _merge Merge_D1
tab Merge_D1
duplicates report seqn
save,replace
```

### DR2TOT merge

```{stata}
use "data\NHANES0910_merged.dta", clear
merge 1:1 seqn using "temp\2009-2010\DR2TOT_F.dta"
rename _merge Merge_D2
tab Merge_D2
duplicates report seqn
save,replace
```

## 2011-2012

Starting with the demographics file.

### BMX merge

```{stata}
use "temp\2011-2012\DEMO_G.dta", clear
save "data\NHANES1112_merged.dta",replace
merge 1:1 seqn using "temp\2011-2012\BMX_G.dta"
rename _merge Merge_BM
tab Merge_BM
duplicates report seqn
save,replace
```

### ALQ merge

```{stata}
use "data\NHANES1112_merged.dta", clear
merge 1:1 seqn using "temp\2011-2012\ALQ_G.dta"
rename _merge Merge_AL
tab Merge_AL
duplicates report seqn
save,replace
```

### BPX merge

```{stata}
use "data\NHANES1112_merged.dta", clear
merge 1:1 seqn using "temp\2011-2012\BPX_G.dta"
rename _merge Merge_BP
tab Merge_BP
duplicates report seqn
save,replace
```

### DUQ merge

```{stata}
use "data\NHANES1112_merged.dta", clear
merge 1:1 seqn using "temp\2011-2012\DUQ_G.dta"
rename _merge Merge_DU
tab Merge_DU
duplicates report seqn
save,replace
```

### SMQ merge

```{stata}
use "data\NHANES1112_merged.dta", clear
merge 1:1 seqn using "temp\2011-2012\SMQ_G.dta"
rename _merge Merge_SM
tab Merge_SM
duplicates report seqn
save,replace
```

### DR1TOT merge

```{stata}
use "data\NHANES1112_merged.dta", clear
merge 1:1 seqn using "temp\2011-2012\DR1TOT_G.dta"
rename _merge Merge_D1
tab Merge_D1
duplicates report seqn
save,replace
```

### DR2TOT merge

```{stata}
use "data\NHANES1112_merged.dta", clear
merge 1:1 seqn using "temp\2011-2012\DR2TOT_G.dta"
rename _merge Merge_D2
tab Merge_D2
duplicates report seqn
save,replace
```

## 2013-2014

Starting with the demographics file.

### BMX merge

```{stata}
use "temp\2013-2014\DEMO_H.dta", clear
save "data\NHANES1314_merged.dta",replace
merge 1:1 seqn using "temp\2013-2014\BMX_H.dta"
rename _merge Merge_BM
tab Merge_BM
duplicates report seqn
save,replace
```

### ALQ merge

```{stata}
use "data\NHANES1314_merged.dta", clear
merge 1:1 seqn using "temp\2013-2014\ALQ_H.dta"
rename _merge Merge_AL
tab Merge_AL
duplicates report seqn
save,replace
```

### BPX merge

```{stata}
use "data\NHANES1314_merged.dta", clear
merge 1:1 seqn using "temp\2013-2014\BPX_H.dta"
rename _merge Merge_BP
tab Merge_BP
duplicates report seqn
save,replace
```

### DUQ merge

```{stata}
use "data\NHANES1314_merged.dta", clear
merge 1:1 seqn using "temp\2013-2014\DUQ_H.dta"
rename _merge Merge_DU
tab Merge_DU
duplicates report seqn
save,replace
```

### SMQ merge

```{stata}
use "data\NHANES1314_merged.dta", clear
merge 1:1 seqn using "temp\2013-2014\SMQ_H.dta"
rename _merge Merge_SM
tab Merge_SM
duplicates report seqn
save,replace
```

### DR1TOT merge

```{stata}
use "data\NHANES1314_merged.dta", clear
merge 1:1 seqn using "temp\2013-2014\DR1TOT_H.dta"
rename _merge Merge_D1
tab Merge_D1
duplicates report seqn
save,replace
```

### DR2TOT merge

```{stata}
use "data\NHANES1314_merged.dta", clear
merge 1:1 seqn using "temp\2013-2014\DR2TOT_H.dta"
rename _merge Merge_D2
tab Merge_D2
duplicates report seqn
save,replace
```

## 2015-2016

Starting with the demographics file.

### BMX merge

```{stata}
use "temp\2015-2016\DEMO_I.dta", clear
save "data\NHANES1516_merged.dta",replace
merge 1:1 seqn using "temp\2015-2016\BMX_I.dta"
rename _merge Merge_BM
tab Merge_BM
duplicates report seqn
save,replace
```

### ALQ merge

```{stata}
use "data\NHANES1516_merged.dta", clear
merge 1:1 seqn using "temp\2015-2016\ALQ_I.dta"
rename _merge Merge_AL
tab Merge_AL
duplicates report seqn
save,replace
```

### BPX merge

```{stata}
use "data\NHANES1516_merged.dta", clear
merge 1:1 seqn using "temp\2015-2016\BPX_I.dta"
rename _merge Merge_BP
tab Merge_BP
duplicates report seqn
save,replace
```

### DUQ merge

```{stata}
use "data\NHANES1516_merged.dta", clear
merge 1:1 seqn using "temp\2015-2016\DUQ_I.dta"
rename _merge Merge_DU
tab Merge_DU
duplicates report seqn
save,replace
```

### SMQ merge

```{stata}
use "data\NHANES1516_merged.dta", clear
merge 1:1 seqn using "temp\2015-2016\SMQ_I.dta"
rename _merge Merge_SM
tab Merge_SM
duplicates report seqn
save,replace
```

### DR1TOT merge

```{stata}
use "data\NHANES1516_merged.dta", clear
merge 1:1 seqn using "temp\2015-2016\DR1TOT_I.dta"
rename _merge Merge_D1
tab Merge_D1
duplicates report seqn
save,replace
```

### DR2TOT merge

```{stata}
use "data\NHANES1516_merged.dta", clear
merge 1:1 seqn using "temp\2015-2016\DR2TOT_I.dta"
rename _merge Merge_D2
tab Merge_D2
duplicates report seqn
save,replace
```

## 2017-2018

Starting with the demographics file, DEMO_J, and merging with the body measures file, BMX_J

### BMX merge

```{stata}
use "temp\2017-2018\DEMO_J.dta", clear
save "data\NHANES1718_merged.dta",replace
merge 1:1 seqn using "temp\2017-2018\BMX_J.dta"
rename _merge Merge_BM
tab Merge_BM
duplicates report seqn
save,replace
```


### ALQ merge

```{stata}
use "data\NHANES1718_merged.dta", clear
merge 1:1 seqn using "temp\2017-2018\ALQ_J.dta"
rename _merge Merge_AL
tab Merge_AL
duplicates report seqn
save,replace
```

### BPX merge

```{stata}
use "data\NHANES1718_merged.dta", clear
merge 1:1 seqn using "temp\2017-2018\BPX_J.dta"
rename _merge Merge_BP
tab Merge_BP
duplicates report seqn
save,replace
```

### DUQ merge

```{stata}
use "data\NHANES1718_merged.dta", clear
merge 1:1 seqn using "temp\2017-2018\DUQ_J.dta"
rename _merge Merge_DU
tab Merge_DU
duplicates report seqn
save,replace
```

### SMQ merge

```{stata}
use "data\NHANES1718_merged.dta", clear
merge 1:1 seqn using "temp\2017-2018\SMQ_J.dta"
rename _merge Merge_SM
tab Merge_SM
duplicates report seqn
save,replace
```

### DR1TOT merge

```{stata}
use "data\NHANES1718_merged.dta", clear
merge 1:1 seqn using "temp\2017-2018\DR1TOT_J.dta"
rename _merge Merge_D1
tab Merge_D1
duplicates report seqn
save,replace
```

### DR2TOT merge

```{stata}
use "data\NHANES1718_merged.dta", clear
merge 1:1 seqn using "temp\2017-2018\DR2TOT_J.dta"
rename _merge Merge_D2
tab Merge_D2
duplicates report seqn
save,replace
```

# Appending datasets

```{stata}
use "data\NHANES0506_merged.dta", clear
save "data\NHANES0518.dta",replace
append using "data\NHANES0708_merged.dta"
append using "data\NHANES0910_merged.dta"
append using "data\NHANES1112_merged.dta"
append using "data\NHANES1314_merged.dta"
append using "data\NHANES1516_merged.dta"
append using "data\NHANES1718_merged.dta"

duplicates report seqn

save,replace
```

```{stata}
use "data\NHANES0518.dta", clear

merge 1:1 seqn using "data\HEI2015R_00518.dta", keep(match master)
rename _merge Merge_HEI
tab Merge_HEI
duplicates report seqn

save, replace
```

