---
title: "Effect MEasure Modification"
author: "Bryon Langford, Matthew Hoctor"
date: "7/21/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (Sys.info()["sysname"] == "Windows") 
  knitr::opts_chunk$set(engine.path = list(stata = "C:/Program Files/Stata17/StataBE-64")) 
if ((Sys.info()["sysname"] == "Darwin"))
  knitr::opts_chunk$set(engine.path = list(stata = "/Applications/Stata/StataIC"))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

# Final Model (with mediators)

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ gndr i.AL_cat bmxbmi ridageyr, or
```

# Model 2 (without mediators)

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ gndr ridageyr, or
```

# Gender EMM analysis

## Full model (Model 3)

### Stratified Analysis

#### Men

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): logit BP_cat i.MJ gndr i.AL_cat bmxbmi ridageyr, or
```

#### Women

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): logit BP_cat i.MJ gndr i.AL_cat bmxbmi ridageyr, or
```

### Interaction Analysis

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ*gndr gndr i.AL_cat bmxbmi ridageyr, or
```

#### previous use lincom

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ*gndr gndr i.AL_cat bmxbmi ridageyr, or

# long form
lincom (1*_IMJ_1 + 0*_IMJ_2 + 0*_IMJ_3 + 0*_IMJ_4 + 1*gndr + 1*_IMJXgndr_1 + 0*_IMJXgndr_2 + 0*_IMJXgndr_3 + 0*_IMJXgndr_4) - (1*_IMJ_1 + 0*_IMJ_2 + 0*_IMJ_3 + 0*_IMJ_4 + 0*gndr + 0*_IMJXgndr_1 + 0*_IMJXgndr_2 + 0*_IMJXgndr_3 + 0*_IMJXgndr_4)

# reduced form
lincom gndr + _IMJXgndr_1
```

#### light use lincom

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ*gndr gndr i.AL_cat bmxbmi ridageyr, or

# long form
lincom (0*_IMJ_1 + 1*_IMJ_2 + 0*_IMJ_3 + 0*_IMJ_4 + 1*gndr + 0*_IMJXgndr_1 + 1*_IMJXgndr_2 + 0*_IMJXgndr_3 + 0*_IMJXgndr_4) - (0*_IMJ_1 + 1*_IMJ_2 + 0*_IMJ_3 + 0*_IMJ_4 + 0*gndr + 0*_IMJXgndr_1 + 0*_IMJXgndr_2 + 0*_IMJXgndr_3 + 0*_IMJXgndr_4)

# reduced form
lincom gndr + _IMJXgndr_2
```

#### moderate use lincom

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ*gndr gndr i.AL_cat bmxbmi ridageyr, or

# long form
lincom (0*_IMJ_1 + 0*_IMJ_2 + 1*_IMJ_3 + 0*_IMJ_4 + 1*gndr + 0*_IMJXgndr_1 + 0*_IMJXgndr_2 + 1*_IMJXgndr_3 + 0*_IMJXgndr_4) - (0*_IMJ_1 + 0*_IMJ_2 + 1*_IMJ_3 + 0*_IMJ_4 + 0*gndr + 0*_IMJXgndr_1 + 0*_IMJXgndr_2 + 0*_IMJXgndr_3 + 0*_IMJXgndr_4)

# reduced form
lincom gndr + _IMJXgndr_3
```

#### heavy use lincom

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ*gndr gndr i.AL_cat bmxbmi ridageyr, or

# long form
lincom (0*_IMJ_1 + 0*_IMJ_2 + 0*_IMJ_3 + 1*_IMJ_4 + 1*gndr + 0*_IMJXgndr_1 + 0*_IMJXgndr_2 + 0*_IMJXgndr_3 + 1*_IMJXgndr_4) - (0*_IMJ_1 + 0*_IMJ_2 + 0*_IMJ_3 + 1*_IMJ_4 + 0*gndr + 0*_IMJXgndr_1 + 0*_IMJXgndr_2 + 0*_IMJXgndr_3 + 0*_IMJXgndr_4)

# reduced form
lincom gndr + _IMJXgndr_4
```


## Model 2 EMM analysis (Without mediators)

### Stratified Analysis

#### Men

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): logit BP_cat i.MJ gndr ridageyr, or
```

#### Women

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): logit BP_cat i.MJ gndr ridageyr, or
```

### Interaction Analysis

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ*gndr gndr ridageyr, or
```

#### previous use lincom

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ*gndr gndr ridageyr, or

# long form
lincom (1*_IMJ_1 + 0*_IMJ_2 + 0*_IMJ_3 + 0*_IMJ_4 + 1*gndr + 1*_IMJXgndr_1 + 0*_IMJXgndr_2 + 0*_IMJXgndr_3 + 0*_IMJXgndr_4) - (1*_IMJ_1 + 0*_IMJ_2 + 0*_IMJ_3 + 0*_IMJ_4 + 0*gndr + 0*_IMJXgndr_1 + 0*_IMJXgndr_2 + 0*_IMJXgndr_3 + 0*_IMJXgndr_4)

# reduced form
lincom gndr + _IMJXgndr_1
```

#### light use lincom

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ*gndr gndr ridageyr, or

# long form
lincom (0*_IMJ_1 + 1*_IMJ_2 + 0*_IMJ_3 + 0*_IMJ_4 + 1*gndr + 0*_IMJXgndr_1 + 1*_IMJXgndr_2 + 0*_IMJXgndr_3 + 0*_IMJXgndr_4) - (0*_IMJ_1 + 1*_IMJ_2 + 0*_IMJ_3 + 0*_IMJ_4 + 0*gndr + 0*_IMJXgndr_1 + 0*_IMJXgndr_2 + 0*_IMJXgndr_3 + 0*_IMJXgndr_4)

# reduced form
lincom gndr + _IMJXgndr_2
```

#### moderate use lincom

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ*gndr gndr ridageyr, or

# long form
lincom (0*_IMJ_1 + 0*_IMJ_2 + 1*_IMJ_3 + 0*_IMJ_4 + 1*gndr + 0*_IMJXgndr_1 + 0*_IMJXgndr_2 + 1*_IMJXgndr_3 + 0*_IMJXgndr_4) - (0*_IMJ_1 + 0*_IMJ_2 + 1*_IMJ_3 + 0*_IMJ_4 + 0*gndr + 0*_IMJXgndr_1 + 0*_IMJXgndr_2 + 0*_IMJXgndr_3 + 0*_IMJXgndr_4)

# reduced form
lincom gndr + _IMJXgndr_3
```

#### heavy use lincom

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_cat i.MJ*gndr gndr ridageyr, or

# long form
lincom (0*_IMJ_1 + 0*_IMJ_2 + 0*_IMJ_3 + 1*_IMJ_4 + 1*gndr + 0*_IMJXgndr_1 + 0*_IMJXgndr_2 + 0*_IMJXgndr_3 + 1*_IMJXgndr_4) - (0*_IMJ_1 + 0*_IMJ_2 + 0*_IMJ_3 + 1*_IMJ_4 + 0*gndr + 0*_IMJXgndr_1 + 0*_IMJXgndr_2 + 0*_IMJXgndr_3 + 0*_IMJXgndr_4)

# reduced form
lincom gndr + _IMJXgndr_4
```

# Age

To be calculated later
