---
title: "Effect Measure Modification"
author: "Bryon Langford, Matthew Hoctor"
date: "7/21/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (Sys.info()["sysname"] == "Windows") 
  knitr::opts_chunk$set(engine.path = list(stata = "C:/Program Files/Stata17/StataBE-64")) 
if ((Sys.info()["sysname"] == "Darwin"))
  knitr::opts_chunk$set(engine.path = list(stata = "/Applications/Stata/StataIC"))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

# Polytomous Models

From [model building 3](https://matthew-hoctor.github.io/Marijuana-HTN---EPI536/Model_Building3.html) using the collapsed MJ exposure variable, MJ2.

## Model 1: crude model

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2, rrr
```

## Model 2 Final Model (without mediators)

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr  ridageyr, rrr
```

## Model 3 Final Model (with mediators)

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr ridageyr i.AL_cat bmxbmi, rrr
```

# Gender EMM Analysis

## Model 1

### Stratified Analysis

#### Men

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): mlogit BP_cat i.MJ2, rrr
```

#### Women

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): mlogit BP_cat i.MJ2, rrr
```

### Interaction Analysis

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr i.MJ2*gndr, rrr
```

## Model 2

### Stratified Analysis

#### Men

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): mlogit BP_cat i.MJ2 ridageyr, rrr
```

#### Women

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): mlogit BP_cat i.MJ2 ridageyr, rrr
```

### Interaction Analysis

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr i.MJ2*gndr ridageyr, rrr
```

### Results

One interaction term was significant, the gender-light-moderate-use interaction term for elevated blood pressure.  Other interaction terms were not significant.  Women had RR of elevated BP given light-moderate MJ use of 1.07 (0.81, 1.42), whereas men had RR of elevated BP given light-moderate MJ use of 1.19 (1.00, 1.43).

## Model 3

### Stratified Analysis

#### Men

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): mlogit BP_cat i.MJ2 ridageyr i.AL_cat bmxbmi SMK_cat, rrr
```

#### Women

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): mlogit BP_cat i.MJ2 ridageyr i.AL_cat bmxbmi SMK_cat, rrr
```

### Interaction Analysis

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr i.MJ2*gndr ridageyr i.AL_cat bmxbmi SMK_cat, rrr
```

# Conventional Logistic Regression 

## Models

### M1

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2, or
```

### M2

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2 gndr ridageyr, or
```

### M3

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2 gndr ridageyr i.AL_cat bmxbmi, or
```

## Interaction Analysis

### M1

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2 gndr i.MJ2*gndr, or
```

### M2

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2  gndr i.MJ2*gndr ridageyr, or
```

### M3

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2  gndr i.MJ2*gndr ridageyr i.AL_cat bmxbmi, or
```


