---
title: "Model Building"
author: "Bryon Langford, Matthew Hoctor"
date: "7/21/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (Sys.info()["sysname"] == "Windows") 
  knitr::opts_chunk$set(engine.path = list(stata = "C:/Program Files/Stata17/StataBE-64")) 
if ((Sys.info()["sysname"] == "Darwin"))
  knitr::opts_chunk$set(engine.path = list(stata = "/Applications/Stata/StataIC"))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

Model Building by Deletion

# Test Proportional Odds Assumption

A significant result of the score test (AKA Lagrange multiplier test) indicates that the assumption of proportional odds does not hold, in which case multinomial logistic regression must be used instead of ordinal logistic regression.

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): omodel mlogit BP_cat i.MJ gndr i.EDUC_cat i.race_eth indfmpir ridageyr
```

Because the omodel function does not support survey data, multinomial logistic regression must be used instead of ordinal logistic regression.

# Full Model

This model includes 

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ gndr i.EDUC_cat i.race_eth indfmpir ridageyr
```

Store full model ORs in a matrix for future:

```{r}
data.0 <- c(-.0363006,-.0041059,.2927856,.2812502,-.0717828,-.0207673,-.1160899,-.0415222,-.0026754,.0110587,.0035981,-.019241)
m.0 <- matrix(data.0, nrow = 3, ncol = 4, byrow = TRUE)
m.0
OR.0 <- exp(m.0)
OR.0
```

# Deletion Cycle 1

As gender is a political variable, it will not be considered for removal.

## Education

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ gndr i.race_eth indfmpir ridageyr
```

```{r}
data.E <- c(-.0259609,.0306447,.3333996,.3272004,-.0580872,.0137353,-.0749648,.004502,.0114964,.0560183,.0541847,.034036)
m.E <- matrix(data.E, nrow = 3, ncol = 4, byrow = TRUE)
#m.E
OR.E <- exp(m.E)
OR.E
```

```{r}
D_OR <- (OR.0-OR.E)/OR.0
100*D_OR
100*mean(abs(D_OR))
```

## Race/Ethnicity

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ gndr i.EDUC_cat indfmpir ridageyr
```


```{r}
data.R <- c(-.0302624, .0128038,.3171098,.2975759,-.0594694   ,.0109809, -.0724136,-.0099068,-.0225278,.0359059,.0292962,-.029817)
m.R <- matrix(data.R, nrow = 3, ncol = 4, byrow = TRUE)
#m.R
OR.R <- exp(m.R)
OR.R
```

```{r}
D_OR <- (OR.0-OR.R)/OR.0
100*D_OR
100*mean(abs(D_OR))
```

## Income

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ gndr i.EDUC_cat i.race_eth ridageyr
```

```{r}
data.I <- c(-.0343907,.0116518,.3211071,.2006977,-.0769204, .0046071,-.1511093,-.139263,-.0139708,.0652252, .0515842,.0095457)
m.I <- matrix(data.I, nrow = 3, ncol = 4, byrow = TRUE)
#m.I
OR.I <- exp(m.I)
OR.I
```

```{r}
D_OR <- (OR.0-OR.I)/OR.0
100*D_OR
100*mean(abs(D_OR))
```

## Age

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ gndr i.EDUC_cat i.race_eth indfmpir
```

```{r}
data.A <- c(-.0425472, -.1292948,.165799,.1728389,-.0772219,-.2250079,-.3344453,-.2296752,-.0113785,-.3217282,-.3938527,-.3773404)
m.A <- matrix(data.A, nrow = 3, ncol = 4, byrow = TRUE)
#m.A
OR.A <- exp(m.A)
OR.A
```

```{r}
D_OR <- (OR.0-OR.A)/OR.0
100*D_OR
100*mean(abs(D_OR))
```

## Result

Of the variables above, race has the least average change in OR; it will be excluded from the next cycle.

```{r}
OR.1 <- OR.R
```

# Deletion Cycle 2

## Education

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ gndr indfmpir ridageyr
```

```{r}
data.E <- c(-.0198477,.0475298,.3575815,.3436251,-.0386858,.0536644,-.0218283,.0459204, -.0025774,.0900549,.088156,.0311304)
m.E <- matrix(data.E, nrow = 3, ncol = 4, byrow = TRUE)
#m.E
OR.E <- exp(m.E)
OR.E
```

```{r}
D_OR <- (OR.1-OR.E)/OR.1
100*D_OR
100*mean(abs(D_OR))
```

## Income

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ gndr i.EDUC_cat ridageyr
```

```{r}
data.I <-  c(-.0237849, .0333968,.3524385,.2235829,-.063084,.0397107,-.1019097,-.1035826,-.0446323, .0943642,.0842452,.0039705)
m.I <- matrix(data.I, nrow = 3, ncol = 4, byrow = TRUE)
#m.I
OR.I <- exp(m.I)
OR.I
```

```{r}
D_OR <- (OR.1-OR.I)/OR.1
100*D_OR
100*mean(abs(D_OR))
```

## Age

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ gndr i.EDUC_cat indfmpir
```

```{r}
data.A <-  c(-.0251341,-.1032825, .1999113,.1994269,-.0465438,-.1791071,-.2729503,-.1801132,.0007932,-.2554685,-.3034009,-.3234544)
m.A <- matrix(data.A, nrow = 3, ncol = 4, byrow = TRUE)
#m.A
OR.A <- exp(m.A)
OR.A
```

```{r}
D_OR <- (OR.1-OR.A)/OR.1
100*D_OR
100*mean(abs(D_OR))
```

## Result

Of the variables above, income has the least average change in OR; it will be excluded from the next cycle.

```{r}
OR.2 <- OR.I
```

# Deletion Cycle 3

 c(111,222,333,444,222,222,333,444,333,222,333,444)

## Education

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ gndr  ridageyr
```

```{r}
data.E <- c(-.0227526,.0797134,.4072004,.2865253,-.0499135,.0921278,-.0401177,-.0355165,-.0548756,.1690277,.1638104,.0852999)
m.E <- matrix(data.E, nrow = 3, ncol = 4, byrow = TRUE)
#m.E
OR.E <- exp(m.E)
OR.E
```

```{r}
D_OR <- (OR.2-OR.E)/OR.2
100*D_OR
100*mean(abs(D_OR))
```

## Age

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ gndr i.EDUC_cat 
```

```{r}
data.A <-  c(-.0095226,-.092097,.2123234,.1139486,-.0340005,-.1676792,-.3426363,-.2926804,.0039307,-.2306821,-.3168202,-.3181186)
m.A <- matrix(data.A, nrow = 3, ncol = 4, byrow = TRUE)
#m.A
OR.A <- exp(m.A)
OR.A
```

```{r}
D_OR <- (OR.2-OR.A)/OR.2
100*D_OR
100*mean(abs(D_OR))
```

## Result

Of the variables above, education has the least average change in OR; it will be excluded from the next cycle.

```{r}
OR.3 <- OR.E
```

# Deletion Cycle 4

## Age

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ gndr i.EDUC_cat 
```

```{r}
data.A <-  c(-.0095226,-.092097,.2123234,.1139486,-.0340005,-.1676792,-.3426363,-.2926804,.0039307,-.2306821,-.3168202,-.3181186)
m.A <- matrix(data.A, nrow = 3, ncol = 4, byrow = TRUE)
#m.A
OR.A <- exp(m.A)
OR.A
```

```{r}
D_OR <- (OR.3-OR.A)/OR.3
100*D_OR
100*mean(abs(D_OR))
```

## Result

Of the variables above, no average change of less than 10% is found.  Therefore the model from deletion cycle 3 is the final model.

# Results

Model 1 will be the crude model, examining BP category only as a function of MJ use category; model 2 will include gender and age as confounders; and model 3 will include gender and age, as well as all mediators (tobacco use, alcohol use, diet, & BMI).

