---
title: "Collapsed Model Building"
author: "Bryon Langford, Matthew Hoctor"
date: "7/21/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (Sys.info()["sysname"] == "Windows") 
  knitr::opts_chunk$set(engine.path = list(stata = "C:/Program Files/Stata17/StataBE-64")) 
if ((Sys.info()["sysname"] == "Darwin"))
  knitr::opts_chunk$set(engine.path = list(stata = "/Applications/Stata/StataIC"))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

The current round of model building uses the collapsed MJ exposure variable

# Full Model

This model includes 

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr i.EDUC_cat i.race_eth indfmpir ridageyr,rrr
```

Store full model RRs in a matrix for future:

```{r}
data.0 <- c(1.081166   ,1.351174,1.002551   ,.9995363,1.010595,.9817426)
RR0 <- matrix(data.0, nrow = 3, ncol = 2, byrow = TRUE)
RR0
```

# Deletion Cycle 1

As gender is a political variable, it will not be considered for removal.

## Education

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr i.race_eth indfmpir ridageyr,rrr
```

```{r}
data.E <- c( 1.114028   ,1.406301   ,1.030628    ,1.038105   ,1.049833   ,1.027226    )
RR.E <- matrix(data.E, nrow = 3, ncol = 2, byrow = TRUE)
RR.E
```

```{r}
D_RR <- (RR0-RR.E)/RR0
100*D_RR
100*mean(abs(D_RR))
```

## Race/Ethnicity

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr i.EDUC_cat indfmpir ridageyr,rrr
```


```{r}
data.R <-c(1.097158   ,1.368162    ,1.029004    ,1.022993,1.047966   ,.9823627)
RR.R <- matrix(data.R, nrow = 3, ncol = 2, byrow = TRUE)
RR.R
```

```{r}
D_RR <- (RR0-RR.R)/RR0
100*D_RR
100*mean(abs(D_RR))
```

## Income

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr i.EDUC_cat i.race_eth ridageyr,rrr
```

```{r}
data.I <- c(1.100949,1.245111   ,1.020784    ,.9092115,1.072668,1.017075)
RR.I <- matrix(data.I, nrow = 3, ncol = 2, byrow = TRUE)
RR.I
```

```{r}
D_RR <- (RR0-RR.I)/RR0
100*D_RR
100*mean(abs(D_RR))
```

## Age

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr i.EDUC_cat i.race_eth indfmpir,rrr
```

```{r}
data.A <- c(.9571534,1.216895,.8176119,.8307283,.719317,.6899826)
RR.A <- matrix(data.A, nrow = 3, ncol = 2, byrow = TRUE)
RR.A
```

```{r}
D_RR <- (RR0-RR.A)/RR0
100*D_RR
100*mean(abs(D_RR))
```

## Result

Of the variables above, race has the least average change in RR; it will be excluded from the next cycle.

```{r}
RR.1 <- RR.R
```

# Deletion Cycle 2

c(111,222,222,222,333,222)

## Education

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr indfmpir ridageyr,rrr
```

```{r}
data.E <- c(1.130602   ,1.424398   ,1.062758    ,1.068938   ,1.095178,1.032786   )
RR.E <- matrix(data.E, nrow = 3, ncol = 2, byrow = TRUE)
RR.E
```

```{r}
D_RR <- (RR.1-RR.E)/RR.1
100*D_RR
100*mean(abs(D_RR))
```

## Income

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr i.EDUC_cat ridageyr,rrr
```

```{r}
data.I <-  c(1.120333   ,1.265921   ,1.050681   ,.9334824,1.124236    ,1.028818    )
RR.I <- matrix(data.I, nrow = 3, ncol = 2, byrow = TRUE)
RR.I
```

```{r}
D_RR <- (RR.1-RR.I)/RR.1
100*D_RR
100*mean(abs(D_RR))
```

## Age

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr i.EDUC_cat indfmpir,rrr
```

```{r}
data.A <-  c(.9741474,1.237044   ,.8432503,.8569868,.7669189,.7231507)
RR.A <- matrix(data.A, nrow = 3, ncol = 2, byrow = TRUE)
RR.A
```

```{r}
D_RR <- (RR.1-RR.A)/RR.1
100*D_RR
100*mean(abs(D_RR))
```

## Result

Of the variables above, education has the least average change in RR; it will be excluded from the next cycle.

```{r}
RR.2 <- RR.E
```

# Deletion Cycle 3

c(111,222,222,222,333,222)

## Income

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr ridageyr,rrr
```

```{r}
data.I <- c(1.174563   ,1.347399    ,1.100645,.991614,1.218877   ,1.122065   )
RR.I <- matrix(data.I, nrow = 3, ncol = 2, byrow = TRUE)
RR.I
```

```{r}
D_RR <- (RR.2-RR.I)/RR.2
100*D_RR
100*mean(abs(D_RR))
```

## Age

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr indfmpir,rrr
```

```{r}
data.A <-  c(1.001713   ,1.28306   ,.8688678,.8923507,.7980226,.7616256)
RR.A <- matrix(data.A, nrow = 3, ncol = 2, byrow = TRUE)
RR.A
```

```{r}
D_RR <- (RR.2-RR.A)/RR.2
100*D_RR
100*mean(abs(D_RR))
```

## Result

Of the variables above, income has the least average change in RR; it will be excluded from the next cycle.

```{r}
RR.3 <- RR.I
```

# Deletion Cycle 4

c(111,222,222,222,333,222)

## Age

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr,rrr
```

```{r}
data.A <-  c(1.024774      ,1.191097      ,.8685494,.7976393,.8321702,.7859162)
RR.A <- matrix(data.A, nrow = 3, ncol = 2, byrow = TRUE)
RR.A
```

```{r}
D_RR <- (RR.3-RR.A)/RR.3
100*D_RR
100*mean(abs(D_RR))
```

## Result

Of the variables above, no average change of less than 10% is found.  Therefore the model from deletion cycle 3 is the final model.

# Mediation Analysis

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr  ridageyr, rrr
```

## Smoking

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr  ridageyr i.SMK_cat, rrr
```


```{r}
data.S <-  c(1.12941      ,1.264867      ,1.098333       ,.9869493,1.158231   ,1.043562   )
RR.S <- matrix(data.S, nrow = 3, ncol = 2, byrow = TRUE)
RR.S
```

```{r}
D_RR <- (RR.3-RR.S)/RR.3
100*D_RR
100*mean(abs(D_RR))
```


## Alcohol Use

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr  ridageyr i.AL_cat, rrr
```

```{r}
data.Al <-  c(1.091474   ,1.196777   ,1.07003   ,.9762643,1.096724      ,1.025015   )
RR.Al <- matrix(data.Al, nrow = 3, ncol = 2, byrow = TRUE)
RR.Al
```

```{r}
D_RR <- (RR.3-RR.Al)/RR.3
100*D_RR
100*mean(abs(D_RR))
```

## BMI

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr  ridageyr bmxbmi, rrr
```

```{r}
data.B <-  c(1.280623   ,1.460632   ,1.225362   ,1.098991   ,1.424801   ,1.31562   )
RR.B <- matrix(data.B, nrow = 3, ncol = 2, byrow = TRUE)
RR.B
```

```{r}
D_RR <- (RR.3-RR.B)/RR.3
100*D_RR
100*mean(abs(D_RR))
```

## Health Eating Index

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr  ridageyr hei2015, rrr
```

```{r}
data.H <-  c(1.214348    ,1.364246   ,1.127368   ,1.010226   ,1.238724   ,1.062457   )
RR.H <- matrix(data.H, nrow = 3, ncol = 2, byrow = TRUE)
RR.H
```

```{r}
D_RR <- (RR.3-RR.H)/RR.3
100*D_RR
100*mean(abs(D_RR))
```

## Results

Only BMI produced a mean change in RR greater than 10%; alcohol use produced a mean change in RR of less than 10%, but individual changes were greater than 10%; addition of smoking or healthy eating index did not produce any changes in RR greater than 10%.  Therefore model 3 will include alcohol use and BMI, but not HEI or smoking.

# Results

Model 1 will be the crude model, examining BP category only as a function of MJ use category; model 2 will include gender and age as confounders; and model 3 will include gender and age, as well as all mediators (tobacco use, alcohol use, & BMI).

