---
title: "Table 3 Calculations"
author: "Bryon Langford, Matthew Hoctor"
date: "7/21/2021"
output:
  html_document:
    number_sections: no
    theme: lumen
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (Sys.info()["sysname"] == "Windows") 
  knitr::opts_chunk$set(engine.path = list(stata = "C:/Program Files/Stata17/StataBE-64")) 
if ((Sys.info()["sysname"] == "Darwin"))
  knitr::opts_chunk$set(engine.path = list(stata = "/Applications/Stata/StataIC"))
```

```{r libraries, include=FALSE}
library(Statamarkdown)
```

# Adjusted model

Model 2; from model_building3:

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr ridageyr, rrr
```

# Model 1: Crude

## Women

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): mlogit BP_cat i.MJ2, rrr
```

## Men

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): mlogit BP_cat i.MJ2, rrr
```

## Overall

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2, rrr
```

# Model 2: adjusting for confounders

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr ridageyr, rrr
```

## Women

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): mlogit BP_cat i.MJ2 ridageyr, rrr
```

## Men

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): mlogit BP_cat i.MJ2 ridageyr, rrr
```

## Overall

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr ridageyr, rrr
```

# Model 3: fully adjusted (including mediators)

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 gndr ridageyr i.AL_cat bmxbmi, rrr
```

## Women

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): mlogit BP_cat i.MJ2 ridageyr i.AL_cat bmxbmi, rrr
```

## Men

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): mlogit BP_cat i.MJ2 ridageyr i.AL_cat bmxbmi, rrr
```

## Overall

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): mlogit BP_cat i.MJ2 ridageyr gndr i.AL_cat bmxbmi, rrr
```

# N Tabulation

For Table 3

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

ta gndr MJ2 if include==1
```

# Table 2

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

ta BP_cat MJ_cat if include==1,col 

svy, subpop(if include==1): ta BP_cat MJ_cat,col percent
```

## Men

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

ta BP_cat MJ_cat if include==1 & gndr==1,col 

svy, subpop(if include==1 & gndr==1): ta BP_cat MJ_cat,col percent
```

## Women

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

ta BP_cat MJ_cat if include==1 & gndr==0,col 

svy, subpop(if include==1 & gndr==0): ta BP_cat MJ_cat,col percent
```

# Alternate Table 2 based on collapsed MJ variable

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

ta BP_cat MJ2 if include==1,col 

svy, subpop(if include==1): ta BP_cat MJ2,col percent
```

## Men

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

ta BP_cat MJ2 if include==1 & gndr==1,col 

svy, subpop(if include==1 & gndr==1): ta BP_cat MJ2,col percent
```

## Women

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

ta BP_cat MJ2 if include==1 & gndr==0,col 

svy, subpop(if include==1 & gndr==0): ta BP_cat MJ2,col percent
```

# Table 4

## N Tabulation

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

ta gndr MJ2 if include==1,col 

svy, subpop(if include==1): ta gndr MJ2,col percent
```

## M1

### Overall

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2, or
```

### Male

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): logit BP_abn i.MJ2, or
```

### Female

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): logit BP_abn i.MJ2, or
```

## M2

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2 gndr ridageyr, or
```

### Male

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): logit BP_abn i.MJ2 ridageyr, or
```

### Female

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): logit BP_abn i.MJ2 ridageyr, or
```

## M3

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2 gndr ridageyr i.AL_cat bmxbmi, or
```


### Male

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): logit BP_abn i.MJ2 ridageyr i.AL_cat bmxbmi, or
```

### Female

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): logit BP_abn i.MJ2 ridageyr i.AL_cat bmxbmi, or
```

# T5

Adjusted OR of abnormal blood pressure according to cannabis use: Effect of Adjustment for possible Mediators

## Overall

### Base Model

Model 2

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2 gndr ridageyr, or
```

### BMI

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2 gndr ridageyr bmxbmi, or
```

### HEI 2015

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2 gndr ridageyr hei2015, or
```

### Alcohol Use

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2 gndr ridageyr AL_cat, or
```

### Tobacco use

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1): logit BP_abn i.MJ2 gndr ridageyr SMK_cat, or
```

## Male

### Base Model

Model 2

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): logit BP_abn i.MJ2 gndr ridageyr, or
```

### BMI

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): logit BP_abn i.MJ2 gndr ridageyr bmxbmi, or
```

### HEI 2015

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): logit BP_abn i.MJ2 gndr ridageyr hei2015, or
```

### Alcohol Use

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): logit BP_abn i.MJ2 gndr ridageyr AL_cat, or
```

### Tobacco use

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==1): logit BP_abn i.MJ2 gndr ridageyr SMK_cat, or
```

## Female

### Base Model

Model 2

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): logit BP_abn i.MJ2 gndr ridageyr, or
```

### BMI

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): logit BP_abn i.MJ2 gndr ridageyr bmxbmi, or
```

### HEI 2015

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): logit BP_abn i.MJ2 gndr ridageyr hei2015, or
```

### Alcohol Use

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): logit BP_abn i.MJ2 gndr ridageyr AL_cat, or
```

### Tobacco use

```{stata}
use "data\NHANES0518_new.dta", clear
svyset sdmvpsu [pw=wtmec12yr], strata(sdmvstra)

xi: svy,subpop(if include==1 & gndr==0): logit BP_abn i.MJ2 gndr ridageyr SMK_cat, or
```

